### 2022-09-07 about/vita_small.tex
No longer a student

\sectheader{Personal and Contact Information}

\leftright{Citizen of Canada and Singapore}{2-9602 74th Avenue NW}
\leftright{Email: marcel\_goh@yahoo.ca}{Edmonton, AB T6E 1E6}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: ``Structural properties of conditional Galton--Watson trees.''
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

\sectheader{Graduate-level Coursework}

Higher algebra (categories, groups, modules), functional analysis, quadratic and modular forms, combinatorics,
topology (including some algebraic topology), probabilistic analysis of algorithms.

\sectheader{Research Interests}

Analysis of random discrete structures, analysis and design of algorithms, enumerative combinatorics,
additive combinatorics.

\begingroup\frenchspacing
\papercount=4
\pubbegin P
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

\begingroup\parindent=10pt
\thing (with Jonah Saks)
Alternating-sum statistics for certain sets of integers. {\sl arXiv:2206.12535} (2022), 12~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949} (2021), 15~pp.
\endgroup
\endgroup%end the frenchspacing

\goodbreak
\sectheader{Reports}

\reportcount=5
\pubbegin R
\repitem Structural properties of conditional Galton--Watson trees. M.Sc.~thesis, McGill University
(Montr\'eal, Qu\'ebec, August 2022), $\hbox{\rm vi} + 75$~pp.
\repitem Finding regularity in Tlingit verb prefixes. Semester project report, McGill University
(Montr\'eal, Qu\'ebec, April 2021), 7 pp.
\repitem Grid-building algorithms on manifolds. Summer research report, McGill University (Montr\'eal, Qu\'ebec,
August 2020), 10 pp.
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.
\repitem The OPythn programming language. Software project report, Charles University (Prague,
Czech Republic, June 2019), 10 pp.

\sectheader{Research Experience}

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of the interactive proof assistant Harpoon and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

@@

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\bf Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students were in attendance.
\medbreak

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Meet with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Hold office hours twice a week and responsible for grading of assignments.
\medbreak

@@

\sectheader{Skills}

{\bf Programming Languages}\par
\CEE, OCaml, Python, Java, PostScript, Haskell, Scheme Lisp,  Standard ML, {\tt CWEB}, {\tt MIXAL}, MIPS Assembly.
\medbreak

{\bf Technologies}\par
\UNIX, Vim, \TeX, Git.
\medbreak

{\bf Languages}\par
Fluent: English, French. Proficient: Mandarin, Italian.
\medbreak

\sectheader{Other}

\parindent=10pt
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, A339942, A341822, and A347580
to the On-line Encyclopedia of Integer Sequences.
\medbreak

\filbreak

>>>>

\sectheader{Contact Information}

\leftright{Mobile phone: +1\thinspace\up(825\up)\thinspace 440-0681}{2-9602 74 Avenue NW}
\leftright{Email: marcel\_goh@yahoo.ca}{Edmonton, AB T6E 1E6}

\sectheader{Languages}

Fluent: English, French. Proficient: Mandarin, Italian.

@@

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.0/4.
Thesis: ``Structural properties of conditional Galton--Watson trees.''
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\bf Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons;
around forty graduate-level students were in attendance.
\medbreak

\leftright{\bf Mentor}{\bf January -- April 2022}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Held office hours twice a week and responsible for grading of assignments.
\medbreak

@@

\begingroup\frenchspacing
\papercount=5
\pubbegin P
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. To appear in {\sl Australasian Journal of Combinatorics}, 15~pp.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms} {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

\begingroup\parindent=10pt
\thing (with Jonah Saks)
Alternating-sum statistics for certain sets of integers. {\sl arXiv:2206.12535} (2022), 12~pp.
\endgroup
\endgroup%end the frenchspacing
